Notebook

### 2022-03-04 doc/notebook/notebook.Rmd
Change output format to github_document
Add notes about frog_translocation dataset

---
title: "Notebook"
author: "Roland Knapp"
date: "`r Sys.Date()`"
editor_options:
  markdown:
    mode: gfm
---

@@

-   site_id: site to which frogs were translocated
-   elevation
-   release_date
-   release_day
-   release_year
-   siteid_donor
-   order: first translocation to site = 0, subsequent translocation = 1
-   type: translocation conducted on foot versus by helicopter
-   shore: suitability of shore/bank habitat for frog overwintering
-   pit_tag_ref
-   survival: individual-level estimated survival 1 year following translocation, based on cmr surveys conducted for at least two years post-translocation
-   sex
-   length: at release
-   weight: at release
-   condition: index based on length and weight
-   swab_id
-   bd_load: at release

@@

@@

survival \~ elevation + siteid_donor + release_day + release_year + order + shore + sex + length + condition + log(bdload) \| site_id

@@

>>>>

---
title: "Notebook"
author: "Roland Knapp"
date: "`r Sys.Date()`"
output:
  github_document
---

```{r}
library(tidyverse)
```

@@

-   site_id: site to which frogs were translocated
-   elevation
-   date
-   day
-   year
-   donor
-   order: first translocation to site = 0, subsequent translocation = 1
-   type: translocation conducted on foot versus by helicopter (not included)
-   shore: suitability of shore/bank habitat for frog overwintering
-   pit_tag_ref
-   survival: individual-level estimated survival 1 year following translocation, based on cmr surveys conducted for at least two years post-translocation
-   sex
-   length: at release
-   weight: at release
-   condition: index based on length and weight
-   swab_id
-   bd_load: at release

@@

Frog condition might be problematic because size and residuals are correlated. Specifically, the largest frogs have the largest positive residuals from a weight:length regression line, even after log10 transformation. As such, length and condition are probably not independent.

```{r, fig.width = 3, fig.align = "center"}
read_csv(here::here("data", "clean", "frog_translocation.csv")) %>% 
ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = lm)
```

Another consideration when designing the analysis is that there are 12 records in which bd_load is null. Of these, 9 are from 70413 on 2013-07-15, likely due to a rush to get frogs packaged prior to helicopter arrival. 39 frogs were translocated on that date, so should probably drop the 9 records where bd_load = NA prior to running the analysis. If bd_load is not an important predictor, can run analysis using the full dataset.

@@

survival \~ elevation + shore + day + year + order + donor + sex + length + log(bdload) \| site_id

@@

Final steps before building model (in analysis Rmd):

-   Change to factor: order, day?, year?
-   Standardize variables?
-   Survival: Create 0/1 variable from probabilities. Change to factor?
